### 2023-05-17 analysis/paper/_results.qmd

<!-- May need to limit the list to compounds that were detected in either batch and keep the full list in supplementary materials -->
```{r}
#| label: tbl-compound-detect
#| tbl-cap: "Target compound including whether it was detected (TRUE) or not (FALSE) in each batch, as well as the lower limit of quantitation (LLOQ) in ng. CBD = cannabidiol; CBN = cannabinol; THC = tetrahydrocannabinol; THCA-A = tetrahydrocannabinolic acid A; THCVA = tetrahydrocannabivarin acid."
uhplc_calculus_detect %>%
  left_join(compound_name_abbrev, by = c("compound" = "abbrev")) %>% 
  full_join(lloq, by = c("name" = "compound")) %>%
  mutate(across(batch1:batch2, ~ replace_na(.x, FALSE))) %>%
  filter(!(batch1 == FALSE & batch2 == FALSE)) %>% 
  select(name, batch1, batch2, lloq) %>% 
  arrange(name) %>% 
  knitr::kable(col.names = c("Compound", "Batch 1", "Batch 2", "LLOQ"))
```

>>>>

<!-- May need to limit the list to compounds that were detected in either batch and keep the full list in supplementary materials -->
```{r}
#| label: tbl-compound-detect
#| tbl-cap: "Target compound including whether it was detected (TRUE) or not (FALSE) in each batch, as well as the lower limit of quantitation (LLOQ) in ng. CBD = cannabidiol; CBN = cannabinol; THC = tetrahydrocannabinol; THCA-A = tetrahydrocannabinolic acid A; THCVA = tetrahydrocannabivarin acid."
uhplc_calculus_detect %>%
  left_join(compound_name_abbrev, by = c("compound" = "abbrev")) %>% 
  left_join(lloq, by = c("name" = "compound")) %>%
  mutate(across(batch1:batch2, ~ replace_na(.x, FALSE))) %>%
  filter(!(batch1 == FALSE & batch2 == FALSE)) %>% 
  select(name, batch1, batch2, lloq) %>% 
  arrange(name) %>% 
  knitr::kable(col.names = c("Compound", "Batch 1", "Batch 2", "LLOQ"))
```

### 2023-05-17 analysis/paper/paper.qmd

library(here)
library(readr)
devtools::load_all()

# upload data
metadata <- read_tsv(here("analysis/data/raw_data/metadata.tsv"))
demography <- read_csv(here("analysis/data/raw_data/demography.csv"))
lloq <- read_tsv(here("analysis/data/raw_data/lloq.tsv"))
uhplc_data_comb <- read_csv(here("analysis/data/derived_data/uhplc-data_combined.csv"))
dental_inv <- read_csv(here("analysis/data/raw_data/dental-inv.csv"))
caries <- read_csv(here("analysis/data/raw_data/caries.csv"))
periodont <- read_csv(here("analysis/data/raw_data/periodontitis.csv"))
periap <- read_csv(here("analysis/data/raw_data/periapical.csv"))
#calculus <- read_csv(here("analysis/data/raw_data/calculus.csv"))
calculus_full <- read_csv(here("analysis/data/raw_data/calculus_full.csv"))
sinusitis_clean <- read_csv(here("analysis/data/derived_data/sinusitis_cleaned.csv"))
path_cond_clean <- read_csv(here("analysis/data/derived_data/path-conditions_cleaned.csv"))

source(here("analysis/scripts/setup-qmd.R"))
#source(here("analysis/supplementary-materials/supp-mat.qmd"), local = knitr::knit_global())
# set viridis as default pallette

>>>>

library(here)
#library(readr)
#devtools::load_all()
source(here("analysis/scripts/setup-qmd.R"))
